---
title: "Ramaswamy2021_MIS-C_10x_Bcell"
author: "Anjali Ramaswamy"
date: "3/11/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Libraries

```{r}
library(Seurat)
library(reshape2)
library(tidyverse)
library(ggplot2)
library(ggsignif)
library(dplyr)
library(viridis)
```

# B cell subclustering

Use pbmc object for subclustering - these subclustering steps are optional to reproduce the B cell analysis, as the fully processed B cell dataset is provided below. To run the following pre-processing steps, please download the pbmc dataset (Ramaswamy2021_MIS-C_10x_PBMC)

```{r}
misc.pbmc <- readRDS("shared/FG_uploads/misc_pbmc_final_upload.rds") 
```

Subcluster B-cell PBMC clusters

```{r}
b_clusters <- WhichCells(misc.pbmc, idents = c(5,10,18,22)) #Naive, mem, doublets, plasma cells
misc.bcell.obj <- subset(misc.pbmc, cells = b_clusters)

misc.bcell.list <-SplitObject(misc.bcell.obj, split.by = "orig.ident")

sub_list <- c()

for(i in 1:length(misc.bcell.list)){
  object <- misc.bcell.list[[i]]
  object@assays$integrated <- NULL
  DefaultAssay(object) <- "RNA"
  sub_list[[i]] <- object
}

names(sub_list) <- names(misc.bcell.list)

sub_list[[7]] <- NULL



for (i in 1:length(sub_list)) {
  sub_list[[i]] <- FindVariableFeatures(sub_list[[i]],
                                               selection.method = "vst",
                                               nfeatures = 2000, verbose = FALSE)
}



misc.anchors <- FindIntegrationAnchors(object.list = sub_list, dims = 1:15, reference = c(9,13,22)) # (MIS-C, A.HD, C.HD)
misc.int <- IntegrateData(anchorset = misc.anchors, dims = 1:15)

misc.int <- ScaleData(misc.int, verbose = FALSE)
misc.int <- RunPCA(misc.int, npcs = 30, verbose = FALSE)
plot1 <- ElbowPlot(misc.int)
misc.cluster <- misc.int #save a copy with PCA done for UMAP and clustering later

misc.int <- RunUMAP(misc.int, reduction = "pca", dims = 1:15) #only run the first time
plot2 <- DimPlot(misc.int, reduction = "umap", group.by = "orig.ident") #only run the first time
plot2


## Find neighbors and clusters (louvain) based on PCA, and then run umap

misc.cluster <- FindNeighbors(misc.cluster, dims = 1:15)
misc.cluster <- FindClusters(misc.cluster, resolution = 0.3, random.seed= 10)


colors <- c("#5A5156", "#325A9B", "#F6222E", "#FE00FA", "#16FF32", "#3283FE",
          "#B10DA1", "#B00068", "#1CFFCE", "#90AD1C", "#2ED9FF", "#E4E1E3")


misc.cluster <- RunUMAP(misc.cluster, dims = 1:15) #default is reduction = pca
plot7 <- DimPlot(misc.cluster, reduction = "umap",
                 pt.size =0.5, label = TRUE)

bcell_markers <- FindAllMarkers(misc.cluster, only.pos = TRUE, # for annotation
                                min.pct = 0.25, logfc.threshold = 0.25, assay = "RNA")

bcell_markers


## Feature plotting for annotation

plot9 <- FeaturePlot(object = misc.cluster,
                   features = "rna_JCHAIN",
                     min.cutoff = 0,
                     #                     max.cutoff = 6,
                     pt.size = 0.8,
                     order = TRUE) + theme_classic(base_size = 25)+
  theme(axis.text = element_text(size = 35),
        legend.text = element_text(size = 20),
        plot.title = element_text(size = 45, face= "italic", hjust = 0.5)) +
  ggtitle("JCHAIN")

plot9


## Sample composition

cluster_prop <- table(Idents(misc.cluster), misc.cluster$orig.ident) # this goes into cell type proportion grid

head(cluster_prop)
# original idents can be found as "sequencing ids" in supplementary sample info table



# Single R

library(SingleR)
library(ensembldb)
test <- GetAssayData(misc.cluster)
monaco <- MonacoImmuneData(ensembl=FALSE)
annot <- SingleR(test = test, ref = monaco, labels = monaco$label.fine)
misc.cluster[["SingleR.labels"]] <- annot$labels

plot8 <- DimPlot(misc.cluster, reduction = "umap",
                 cols=DiscretePalette(32, palette='polychrome'),
                 pt.size =0.5,
                 group.by = "SingleR.labels")

plot8

```

# Load in B cell object and plot UMAP

Annotations and metadata updated in the below object

```{r}
misc.bcell <- readRDS("shared/FG_uploads/misc_bcell_final_upload.rds") 

plot8 <- DimPlot(misc.bcell, reduction = "umap",
                 cols=DiscretePalette(32, palette='polychrome'),
                 pt.size =0.5,
                 group.by = "seurat_clusters")

plot8
```

# Dot Plot

```{r}
level.order <- c("Naive B I", "Naive B II", "Intermediate memory", "CD27+IgM+IgG+ memory",
                 "Memory B-cell", "Non-dividing plasma cell", "Dividing plasma cell")

misc.bcell$annotation_bcell <- factor(misc.bcell$annotation_bcell, levels = level.order )

features.bcell <- c("rna_MS4A1", "rna_IGHD", "rna_IGHM", "rna_NR4A1", 
                    "rna_IGHG3", "rna_IGHG2", "rna_IGHG1",  "rna_CD27",
                    "rna_CD38", "rna_JCHAIN", "rna_MZB1", "rna_XBP1", "rna_MKI67")

Idents(misc.cluster) <- "annotation_bcell"

inferno_mod <- inferno(20)[3:20]

dot <- DotPlot(misc.bcell, features = rev(features.bcell),  
               assay = "RNA", dot.scale = 4.5)+ 
  scale_color_gradient2(low = inferno_mod[3], mid = "#D64B40FF", high = "#F1ED6FFF", midpoint = 0.25) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.9, hjust=1, size = 12),
        axis.line = element_line(size = 0.3), axis.ticks = element_line(size = 0.3)) + 
  coord_flip()

dot
```


